---
title: "AI Knowledge Sharing"
subtitle: "Session One"
author: "Riccardo Esclapon"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  revealjs::revealjs_presentation:
    theme: white
    highlight: zenburn
    transition: fade
    center: true
    css: minimalist.css
    self_contained: false
    reveal_plugins: ["zoom"]
    reveal_options:
      slideNumber: false
      controls: false
      progress: false
      minScale: 1
      maxScale: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(palmerpenguins)
```

# Begin

## Embracing AI

<span class="large-text">Transforming how we</span>

<span class="highlight">work</span> • <span class="highlight">think</span> • <span class="highlight">create</span>

<div class="attribution">
Session 1/4
</div>

## Why This Matters

- The AI revolution is accelerating
- Exponential growth in capabilities
- Reshaping entire industries
- Creating new ethical frameworks

<div class="spacer"></div>

Everything changes. Are we ready?

## Evolution of Intelligence

<div class="timeline-minimal">
<div class="time-period">1950s</div>
<div class="time-period">1980s</div>
<div class="time-period">2010s</div>
<div class="time-period">Now</div>
</div>

<div class="quote">
"AI is the new electricity."<br>
<span class="author">— Andrew Ng</span>
</div>

# Fundamentals

## Core Principles {data-transition="slide"}

<div class="principles">
<div class="principle">Data-driven</div>
<div class="principle">Pattern recognition</div>
<div class="principle">Adaptive learning</div>
<div class="principle">Probabilistic reasoning</div>
</div>

## Visual Simplicity

```{r simple-chart}
ggplot(data = penguins, aes(x = flipper_length_mm, y = bill_length_mm, color = species)) +
  geom_point(size = 3, alpha = 0.8) +
  theme_minimal() +
  labs(
    x = "Flipper Length (mm)",
    y = "Bill Length (mm)",
    color = "Species",
    title = NULL
  ) +
  theme(
    legend.position = "bottom",
    text = element_text(family = "Helvetica", size = 14),
    axis.title = element_text(size = 12),
    panel.grid.minor = element_blank()
  )
```

## Three Pillars

<div class="three-cols">
  <div class="col">
    <h3>Machine Learning</h3>
    <p>Pattern recognition from data without explicit programming</p>
  </div>
  <div class="col">
    <h3>Deep Learning</h3>
    <p>Neural networks with multiple layers for complex representations</p>
  </div>
  <div class="col">
    <h3>Reinforcement Learning</h3>
    <p>Learning optimal actions through environmental feedback</p>
  </div>
</div>

# Applications {data-background="#f5f5f5"}

## Transformation Map

<div class="transformation-grid">
  <div class="t-item">Healthcare</div>
  <div class="t-item">Finance</div>
  <div class="t-item">Education</div>
  <div class="t-item">Transportation</div>
  <div class="t-item">Manufacturing</div>
  <div class="t-item">Creative Arts</div>
  <div class="t-item">Agriculture</div>
  <div class="t-item">Energy</div>
  <div class="t-item">Retail</div>
</div>

<div class="micro-note">Every industry is being reimagined</div>

## Case Study: Healthcare

<div class="case-study">
  <div class="cs-item">93% accuracy in cancer detection</div>
  <div class="cs-item">30% reduction in false positives</div>
  <div class="cs-item">2x faster clinical trials</div>
  <div class="cs-item">$200B estimated annual impact</div>
</div>

<div class="citation">Stanford Medicine, 2023</div>

## Success Factors

<ol class="large-list">
  <li>Quality data</li>
  <li>Domain expertise</li>
  <li>Algorithmic innovation</li>
  <li>Computational resources</li>
  <li>Ethical frameworks</li>
</ol>

# Ethics {data-background="#000" data-background-opacity="0.8"}

## Critical Questions {.white-text}

<div class="big-question">Who benefits?</div>
<div class="big-question">Who decides?</div>
<div class="big-question">Who is accountable?</div>

## Principles {.white-text}

<div class="ethics-container">
  <div class="ethics-item">Fairness</div>
  <div class="connecting-line"></div>
  <div class="ethics-item">Transparency</div>
  <div class="connecting-line"></div>
  <div class="ethics-item">Privacy</div>
  <div class="connecting-line"></div>
  <div class="ethics-item">Security</div>
</div>

<div class="attribution">
Building responsible AI requires vigilance
</div>

# Action {data-background-gradient="linear-gradient(135deg, #f5f7fa 0%, #c3cfe2 100%)"}

## Learning Path

<div class="path-container">
  <div class="path-step">Learn foundations</div>
  <div class="path-arrow">→</div>
  <div class="path-step">Apply to your field</div>
  <div class="path-arrow">→</div>
  <div class="path-step">Build solutions</div>
  <div class="path-arrow">→</div>
  <div class="path-step">Share knowledge</div>
</div>

## Resources

<div class="resources-grid">
  <div class="resource-item">
    <span class="resource-title">FastAI</span>
    <span class="resource-desc">Practical Deep Learning</span>
  </div>
  <div class="resource-item">
    <span class="resource-title">Stanford CS224n</span>
    <span class="resource-desc">NLP with Deep Learning</span>
  </div>
  <div class="resource-item">
    <span class="resource-title">DeepLearning.AI</span>
    <span class="resource-desc">Specializations</span>
  </div>
  <div class="resource-item">
    <span class="resource-title">Hugging Face</span>
    <span class="resource-desc">NLP Community</span>
  </div>
</div>

## Next Session

<div class="next-session">
  <div class="ns-date">April 14, 2025</div>
  <div class="ns-title">Advanced Models & Architectures</div>
  <ul class="ns-topics">
    <li>Transformer architectures</li>
    <li>Multimodal learning</li>
    <li>Generative models</li>
  </ul>
</div>

# Thank You {data-background="#fff"}

<div class="contact-info">
  riccardo@example.com<br>
  @riccardo
</div>