---
title: "AI Knowledge Sharing"
subtitle: "Session One: Fundamentals & Applications"
author: "Riccardo Esclapon"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  revealjs::revealjs_presentation:
    theme: night
    highlight: pygments
    transition: slide
    center: true
    css: custom.css
    self_contained: false
    includes:
      in_header: header.html
    reveal_plugins: ["notes", "search", "zoom", "chalkboard"]
    reveal_options:
      slideNumber: true
      previewLinks: true
      progress: true
      chalkboard:
        theme: whiteboard
        toggleNotesButton: false
      menu:
        numbers: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(gganimate)
library(plotly)
library(htmlwidgets)
```

# Welcome {data-background="linear-gradient(to bottom right, #222, #0088cc)"}

## About This Series {.emphasized}

<div class="columns">
<div class="column" width="60%">

This session is the first in our AI Knowledge Sharing series.

- Fundamental concepts in modern AI
- Applications across industries
- Ethical considerations
- Hands-on demonstrations

</div>
<div class="column" width="40%">
<img src="https://via.placeholder.com/400x300" alt="AI Knowledge Sharing">
</div>
</div>

<aside class="notes">
Speaker notes:
- Welcome everyone to our first session
- Explain the goals of the series
- Mention the experience level expected
</aside>

# Fundamentals {data-background-color="#3a0ca3"}

## Evolution of AI {data-transition="zoom"}

<div class="timeline">
<div class="container left">
  <div class="content">
    <h3>1950s</h3>
    <p>The term "Artificial Intelligence" is coined</p>
  </div>
</div>
<div class="container right">
  <div class="content">
    <h3>1980s</h3>
    <p>Expert systems emerge</p>
  </div>
</div>
<div class="container left">
  <div class="content">
    <h3>2010s</h3>
    <p>Deep learning revolution</p>
  </div>
</div>
<div class="container right">
  <div class="content">
    <h3>Present</h3>
    <p>Large language models and multimodal AI</p>
  </div>
</div>
</div>

## Key Concepts {data-transition="slide-in fade-out"}

<div class="concepts">
  <div class="concept-item" onclick="toggleExplanation('ml')">
    <h3>Machine Learning</h3>
    <div id="ml" class="explanation">Systems that learn from data without explicit programming</div>
  </div>
  <div class="concept-item" onclick="toggleExplanation('dl')">
    <h3>Deep Learning</h3>
    <div id="dl" class="explanation">Neural networks with multiple layers that can learn complex patterns</div>
  </div>
  <div class="concept-item" onclick="toggleExplanation('nlp')">
    <h3>NLP</h3>
    <div id="nlp" class="explanation">Natural Language Processing enables computers to understand human language</div>
  </div>
</div>

```{js, echo=FALSE}
function toggleExplanation(id) {
  var x = document.getElementById(id);
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
```

# Applications {data-background="#f72585"}

## Interactive Data Visualization {.interactive}

```{r interactive-plot, echo=FALSE}
# Create an interactive plot
p <- ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  labs(title = "Engine Displacement vs Highway MPG",
       x = "Engine Displacement (L)",
       y = "Highway MPG")

ggplotly(p) %>%
  layout(title = list(text = "Interactive Data Visualization"))
```

## AI in Healthcare {data-transition="convex"}

<div class="box-highlight">
<h3>Impact Areas</h3>
<ul>
  <li class="fragment fade-in">Disease diagnosis from medical imagery</li>
  <li class="fragment fade-in">Drug discovery acceleration</li>
  <li class="fragment fade-in">Personalized treatment plans</li>
  <li class="fragment fade-in">Hospital workflow optimization</li>
</ul>
</div>

<p class="citation">Source: Stanford AI Index Report 2023</p>

# Demonstrations {data-background="#560bad"}

## Real-time AI Analysis {data-state="dynamic"}

<div class="demo-container">
  <div class="demo-input">
    <textarea id="user-input" placeholder="Enter text for analysis..."></textarea>
    <button onclick="analyzeText()">Analyze</button>
  </div>
  <div class="demo-output" id="analysis-result">
    Results will appear here...
  </div>
</div>

```{js, echo=FALSE}
function analyzeText() {
  var text = document.getElementById('user-input').value;
  // This is a mock analysis - in a real presentation, this could connect to an API
  var result = "Sentiment: " + (Math.random() > 0.5 ? "Positive" : "Negative") + "<br>";
  result += "Key entities: " + ["AI", "technology", "data", "learning"].sort(() => .5 - Math.random()).slice(0,2).join(", ");
  document.getElementById('analysis-result').innerHTML = result;
}
```

## Animated ML Process {.animated}

```{r animated-chart, echo=FALSE}
# Create a basic animation of a machine learning process
set.seed(123)
df <- data.frame(
  x = c(rnorm(50, 2, 1), rnorm(50, 4, 1)),
  y = c(rnorm(50, 2, 1), rnorm(50, 4, 1)),
  class = factor(rep(c("A", "B"), each = 50))
)

# Create decision boundary animation
anim <- ggplot(df, aes(x, y, color = class)) +
  geom_point() +
  labs(title = "Decision Boundary Evolution: Iteration {frame} of 20") +
  theme_minimal() +
  transition_states(
    states = 1:20,
    transition_length = 2,
    state_length = 1
  ) +
  enter_fade() +
  exit_fade() +
  shadow_mark(alpha = 0.3)

# In a real presentation, we would use animate() to save this
# For now, we'll just show the static plot
ggplot(df, aes(x, y, color = class)) +
  geom_point() +
  labs(title = "Decision Boundary Example") +
  theme_minimal()
```

# Discussion {data-background="#4361ee"}

## Ethical Considerations {data-transition="fade"}

<div class="grid-layout">
  <div class="grid-item" id="ethics-1">Bias & Fairness</div>
  <div class="grid-item" id="ethics-2">Privacy Concerns</div>
  <div class="grid-item" id="ethics-3">Transparency</div>
  <div class="grid-item" id="ethics-4">Accountability</div>
</div>

<div class="quote-box">
"With great power comes great responsibility."
</div>

## Q&A Session {.centered data-background="#7209b7"}

<div class="question-box">
  <h3>Questions?</h3>
  <p>Use the QR code to submit anonymous questions</p>
  <div class="qr-placeholder">[QR CODE PLACEHOLDER]</div>
</div>

# Thank You {data-background-image="https://via.placeholder.com/1920x1080" data-background-opacity="0.3"}

## Next Sessions {.final-slide}

<div class="next-sessions">
  <div class="session">
    <h3>Session 2</h3>
    <p>Advanced Models & Architectures</p>
    <p class="date">April 14, 2025</p>
  </div>
  <div class="session">
    <h3>Session 3</h3>
    <p>Practical Implementation Strategies</p>
    <p class="date">May 12, 2025</p>
  </div>
  <div class="session">
    <h3>Session 4</h3>
    <p>Future Trends & Opportunities</p>
    <p class="date">June 16, 2025</p>
  </div>
</div>

<p class="contact">Contact: riccardo@example.com | @riccardo</p>